Imposing a Weight Norm Constraint for Neuro–Adaptive Control

### 2025-05-28 presentation/presentation.tex
gif youtube test

\usepackage{svg}

@@

  \textbf{Challenges}
  \small{
    \begin{itemize}
      \item \textbf{Optimality}: In general, the adaptation laws are deriven with respect to the tracking error, which may not guarantee optimal performance.
      \item \textbf{Unpredictable Amplitude of NN Weights}: 
        \begin{itemize}
          \item NN weights may diverge, leading to instability.
          \item This can result in unpredictable behavior of the controller.
        \end{itemize}
      \item \textbf{Parameter Dependency}: 
    \end{itemize}
  }

@@

>>>>

\usepackage{svg}
\usepackage{media9}             %pdflatex, latex+dvips+ps2pdf, xelatex
\usepackage{multimedia}
\usepackage{animate}

@@

  \textbf{Challenges}
  \small{
    \begin{itemize}
      \item \textbf{Optimality}: In general, the adaptation laws are driven with respect to the tracking error, which may not guarantee optimal performance.
      \item \textbf{Unpredictable Amplitude of NN Weights}: 
        \begin{itemize}
          \item NN weights may diverge, leading to instability.
          \item This can result in unpredictable behavior of the controller.
        \end{itemize}
      \item \textbf{Parameter Dependency}: 
    \end{itemize}
  }

@@

  % % \movie[width=3cm,height=2cm,poster]{}{overall.mp4}
  % \begin{figure}
  %   \centering
  %   \href{https://youtu.be/U5uDbJQkGY8}{
  %     \includegraphics[width=.1\textwidth]{figures/KAIST-hi.png}
  %   }
  % \end{figure}

  % \animategraphics[loop,width=4cm]{gifs/overall-}
  \animategraphics[loop,width=4cm]{10}{gifs/overall-}{0}{10}
